GNSS-based displacement detection using Bayesian inference for deformation monitoring

### 2020-11-23 paper/manuscript-iot.tex
proof reading2 complete

	% As a general rule, do not put math, special symbols or citations
	% in the abstract or keywords.
	\begin{abstract}
For decades, deformation monitoring based on the Global navigation satellite system (GNSS) has increasingly been important for a wide range of applications, from landslide monitoring, subsidence survey, to industrial measurement. 
Most of the GNSS-based displacement detection methods in these applications are based on GNSS long-term static positioning results.
With the development of Internet of Things (IOT), high-precision GNSS positioning, and GNSS related transmission protocol, kinematic positioning results can be transmitted to the cloud in real-time.
However, due to the influence of measurement noise, it is still a challenge to identify and extract displacement from GNSS kinematic positioning results in a short time.
To resolve this, we propose a novel displacement detection approach with the purpose of identifying and extracting displacement from GNSS kinematic positioning in a short time.
Specifically, we use the Bayesian inference model to obtain the displacement change time from the coordinate time series of GNSS kinematic positioning. 
%The likelihood function of the observation and the prior distribution of the parameters to be estimated are provided.
%Finally, Bayesian inference was implemented by Markov Chain Monte Carlo (MCMC) sampling.
By investigating the posterior distribution of the designed change point parameter, we can identify the change points.
Furthermore, we derive the mean value from the posterior distribution of the mean parameter, and further obtain the displacement.
Results from simulation and field experiments have demonstrated the effectiveness and flexibility of the proposed method.
For significant displacement, it can be clearly identified; for small displacement, it can be identified by adding an interval constraint prior. The accuracy of up-displacement extraction from GNSS real-time kinematic positioning can reach within 2 mm in 15 minutes.
	\end{abstract}

@@

	\section{Introduction}
	% The very first letter is a 2 line initial drop letter followed
	% by the rest of the first word in caps.
	% 
	% form to use if the first word consists of a single letter:
	% \IEEEPARstart{A}{demo} file is ....
	% 
	% form to use if you need the single drop letter followed by
	% normal text (unknown if ever used by the IEEE):
	% \IEEEPARstart{A}{}demo file is ....
	% 
	% Some journals put the first two words in caps:
	% \IEEEPARstart{T}{his demo} file is ....
	% 
	% Here we have the typical use of a "T" for an initial drop letter
	% and "HIS" in caps to complete the first word.
	\label{intro}
	%全球定位系统系统的应用-》位移探测
	%在自然灾害监测，或者工业测量等领域，GNSS被用于位移探测。
	%传统测量仪器的弊端，GNSS位移探测的优势。
	%GNSS在位移探测中扮演的角色，以及位移探测的要求
	%目前人们对于基于GNSS位移探测的研究更过的关注与如何提高定位的精度，而忽略了如何从GNSS获取的坐标序列中识别并提取位移。
	\IEEEPARstart{I}{n}  recent decades, Global navigation satellite system (GNSS) has been widely used in navigation, surveying, and civil aviation as a positioning method\cite{teunissen2017springer}. 
	Besides, as a displacement detection method in deformation monitoring, GNSS has been applied to natural landslide monitoring\cite{awange2012environmental}, industrial measurement\cite{pavasovic2011application}, and other fields. 
	Compared with traditional displacement detection technology, GNSS-based displacement detection has many advantages, such as real-time, high precision, and weather independence\cite{shen2019a}. 
	%随着物联网通信技术标准的制订和创新，高精度定位技术，例如RTK，PPP，以及GNSS传输协议NTRIP的发展，GNSS定位结果可以被实时传输到云端。
	With the improvement of the Internet of things (IOT), GNSS high-precision positioning technology, and GNSS enhanced information transmission protocol, high-precision GNSS positioning results can be transmitted to the cloud in real-time.
	%Displacement detection involves displacement identification and extraction. 
	GNSS-based displacement detection is generally performed by the time-domain difference of GNSS positioning results\cite{abidin2004use,rs12203375}. 
	There are many researches on displacement detection based on GNSS, which can be divided into two categories.

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[scale=0.35]{v_bd9_4_up_tau}
	\caption{Posterior sample distribution of $\tau$ in field experiment 2.}
	\label{fig_v_bd9_4_up_tau}
\end{figure} 
\begin{figure}[htbp]
	\centering
	\includegraphics[scale=0.35]{v_bd9_4_up_mu}
	\caption{Histogram of posterior sample of $\mu$ in field experiment 2.}
	\label{fig_v_bd9_4_up_mu}
\end{figure} 
\begin{figure}[htbp]
	\centering
	\includegraphics[scale=0.3]{v_bd9_4_up_sigma}
	\caption{Histogram of posterior sample of $\sigma$ in field experiment 2.}
	\label{fig_v_bd9_4_up_sigma}
\end{figure}
Due to the decrease of displacement amplitude, the results are not as good as the previous experimental results. 
It can be seen from Fig. \ref{fig_v_bd9_4_up_tau} that there are two peaks in the posterior sample distribution of $\tau_1$. Unlike Fig. \ref{fig_v_bd9_3_up_tau} of the previous experimental results, the two peaks are far away from each other, exceeding 500 s. 
Accordingly, there are two peaks in the posterior sample distribution of $\mu_0$, $\mu_1$ and $\sigma$. 
In addition, we found that the second peak of $\tau_1$ is very close to the peak of $\tau_2$, which is not what we want because we do not want to get very short segments. 
In the next section, we will discuss adding a prior to the model to improve the performance of Bayesian inference.
\section{Discussion}
\label{disc}
In field experiment 1, there are two significant peaks in the posterior sample distribution at the same change point. 
In addition, in field experiment 2, the posterior distribution interval of two different change points is close.
The interval between adjacent change points is constrained by adding a prior. 
The random variable $d\tau$, the distance between continuous change points, is added, which obeys the  discrete uniform distribution.

>>>>

	% As a general rule, do not put math, special symbols or citations
	% in the abstract or keywords.
	\begin{abstract}
For decades, displacement detection based on the Global navigation satellite system (GNSS) has increasingly been important for a wide range of applications, from landslide monitoring, subsidence survey, to industrial measurement. 
Most of the GNSS-based displacement detection methods in these applications are based on GNSS long-term static positioning results.
With the development of Internet of Things (IoT), high-precision GNSS positioning, and GNSS related transmission protocol, kinematic positioning results can be transmitted to the cloud in real-time.
However, due to the influence of measurement noise, it is still a challenge to identify and extract displacement from GNSS kinematic positioning results in a short time.
To resolve this, we propose a novel displacement detection approach with the purpose of identifying and extracting displacement from GNSS kinematic positioning in a short time.
Specifically, we use the Bayesian inference model to obtain the displacement change time from the coordinate time series of GNSS kinematic positioning. 
%The likelihood function of the observation and the prior distribution of the parameters to be estimated are provided.
%Finally, Bayesian inference was implemented by Markov Chain Monte Carlo (MCMC) sampling.
By investigating the posterior distribution of the designed change point parameter, we can identify the change points.
Furthermore, we derive the mean value from the posterior distribution of the mean parameter, and further obtain the displacement.
Results from simulation and field experiments have demonstrated the effectiveness and flexibility of the proposed method.
For significant displacement, it can be clearly identified; for small displacement, it can be identified by adding an interval constraint prior. The accuracy of up-displacement extraction from GNSS real-time kinematic positioning can reach within 2 mm in 15 minutes.
	\end{abstract}

@@

	\section{Introduction}
	% The very first letter is a 2 line initial drop letter followed
	% by the rest of the first word in caps.
	% 
	% form to use if the first word consists of a single letter:
	% \IEEEPARstart{A}{demo} file is ....
	% 
	% form to use if you need the single drop letter followed by
	% normal text (unknown if ever used by the IEEE):
	% \IEEEPARstart{A}{}demo file is ....
	% 
	% Some journals put the first two words in caps:
	% \IEEEPARstart{T}{his demo} file is ....
	% 
	% Here we have the typical use of a "T" for an initial drop letter
	% and "HIS" in caps to complete the first word.
	\label{intro}
	%全球定位系统系统的应用-》位移探测
	%在自然灾害监测，或者工业测量等领域，GNSS被用于位移探测。
	%传统测量仪器的弊端，GNSS位移探测的优势。
	%GNSS在位移探测中扮演的角色，以及位移探测的要求
	%目前人们对于基于GNSS位移探测的研究更过的关注与如何提高定位的精度，而忽略了如何从GNSS获取的坐标序列中识别并提取位移。
	\IEEEPARstart{I}{n}  recent decades, the Global navigation satellite system (GNSS) has been widely used in surveying\cite{barry2011surveying}, and civil aviation\cite{iatsouk2004development}, and autonomous vehicle\cite{kuutti2018survey} as a positioning method. 
	Besides, as a displacement detection method in deformation monitoring, GNSS has been applied to landslide monitoring\cite{awange2012environmental}, subsidence survey\cite{bian2014monitoring}, industrial measurement\cite{pavasovic2011application}, and other fields. 
	Compared with traditional displacement detection technology, GNSS-based displacement detection has many advantages, such as real-time, high precision, and weather independence\cite{shen2019a}. 
	%随着物联网通信技术标准的制订和创新，高精度定位技术，例如RTK，PPP，以及GNSS传输协议NTRIP的发展，GNSS定位结果可以被实时传输到云端。
	With the development of the Internet of things (IoT), GNSS high-precision positioning technology, and GNSS enhanced information transmission protocol, high-precision GNSS positioning results can be transmitted to the cloud in real-time\cite{mei2019survey}.
	%Displacement detection involves displacement identification and extraction. 
	GNSS-based displacement detection is generally performed by the time-domain difference of GNSS positioning results\cite{abidin2004use,rs12203375}. 
	There are many researches on displacement detection based on GNSS, which can be divided into two categories.

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[scale=0.35]{v_bd9_4_up_tau}
	\caption{Posterior sample distribution of $\tau$ in field experiment 2.}
	\label{fig_v_bd9_4_up_tau}
\end{figure} 
\begin{figure}[htbp]
	\centering
	\includegraphics[scale=0.35]{v_bd9_4_up_mu}
	\caption{Histogram of posterior sample of $\mu$ in field experiment 2.}
	\label{fig_v_bd9_4_up_mu}
\end{figure} 
\begin{figure}[htbp]
	\centering
	\includegraphics[scale=0.3]{v_bd9_4_up_sigma}
	\caption{Histogram of posterior sample of $\sigma$ in field experiment 2.}
	\label{fig_v_bd9_4_up_sigma}
\end{figure}
Due to the decrease of displacement amplitude, the results are not as good as the previous experimental results. 
It can be seen from Fig. \ref{fig_v_bd9_4_up_tau} that there are two peaks in the posterior sample distribution of $\tau_1$. Unlike Fig. \ref{fig_v_bd9_3_up_tau} of the previous experimental results, the two peaks are far away from each other, exceeding 500 s. 
Accordingly, there are two peaks in the posterior sample distribution of $\mu_0$, $\mu_1$ and $\sigma$. 
In addition, we found that the second peak of $\tau_1$ is very close to the peak of $\tau_2$, which is not what we want because we do not want to get very short segments. 
In the next section, we will discuss adding a prior to the model to improve the performance of Bayesian inference.
\section{Discussion}
\label{disc}
In field experiment 1, there are two significant peaks in the posterior sample distribution at the same change point. 
In addition, in field experiment 2, the posterior distribution interval of two different change points is close.
Here, the interval between adjacent change points is constrained by adding a prior. 
A random variable $d\tau$, the distance between continuous change points, is added, which obeys the  discrete uniform distribution.
